The Independence of the Continuum Hypothesis in Isabelle/ZF

### 2022-03-04 src/document/root.tex
Names and Choice_Axiom according to Fm_Definitions.
I've changed some definitions in Names making them more
general; we should decide if are worth-keeping. We should
understand better why the satisfaction for is_check_fm
cannot be in Fm_Definitions.

I've added some text and comments in Fm_Definitions.
Editing deps of Forces_Definition. Missing LaTeX macro
A bit more of (sub)section structure
Comments on Defs_Main and Demonstrations (now in the session). TODOs and several FIXMEs deleted/addressed/transformed. New way to run (see README). Repeated code deleted.

% for uniform font size
%\renewcommand{\isastyle}{\isastyleminor}

\renewcommand{\isacharunderscorekeyword}{\mbox{\_}}
\renewcommand{\isacharunderscore}{\mbox{\_}}
\renewcommand{\isasymtturnstile}{\isamath{\Vdash}}
\renewcommand{\isacharminus}{-}
\newcommand{\axiomas}[1]{\mathit{#1}}
\newcommand{\ZFC}{\axiomas{ZFC}}
\newcommand{\AC}{\axiomas{AC}}
\newcommand{\CH}{\axiomas{CH}}

@@

\title{Formalization of Forcing in Isabelle/ZF}
\author{Emmanuel Gunther\thanks{Universidad Nacional de C\'ordoba. 
    Facultad de Matem\'atica, Astronom\'{\i}a,  F\'{\i}sica y
    Computaci\'on.}
  \and
  Miguel Pagano\footnotemark[1]
  \and
  Pedro S\'anchez Terraf\footnotemark[1] \thanks{Centro de Investigaci\'on y Estudios de Matem\'atica
    (CIEM-FaMAF), Conicet. C\'ordoba. Argentina.
    Supported by Secyt-UNC project 33620180100465CB.}
  \and
  Mat\'{\i}as Steinberg\footnotemark[1]
}
\maketitle

@@

>>>>

% for uniform font size
%\renewcommand{\isastyle}{\isastyleminor}
\newcommand{\forces}{\Vdash}
\newcommand{\dom}{\mathsf{dom}}
\renewcommand{\isacharunderscorekeyword}{\mbox{\_}}
\renewcommand{\isacharunderscore}{\mbox{\_}}
\renewcommand{\isasymtturnstile}{\isamath{\Vdash}}
\renewcommand{\isacharminus}{-}
\newcommand{\session}[1]{\textit{#1}}
\newcommand{\theory}[1]{\texttt{#1}}
\newcommand{\axiomas}[1]{\mathit{#1}}
\newcommand{\ZFC}{\axiomas{ZFC}}
\newcommand{\ZF}{\axiomas{ZF}}
\newcommand{\AC}{\axiomas{AC}}
\newcommand{\CH}{\axiomas{CH}}
\newcommand{\calV}{\mathcal{V}}

@@

\title{The Independence of the Continuum Hypothesis in Isabelle/ZF}
\author{Emmanuel Gunther\thanks{Universidad Nacional de C\'ordoba. 
    Facultad de Matem\'atica, Astronom\'{\i}a,  F\'{\i}sica y
    Computaci\'on.}
  \and
  Miguel Pagano\footnotemark[1]
  \and
  Pedro S\'anchez Terraf\footnotemark[1] \thanks{Centro de Investigaci\'on y Estudios de Matem\'atica
    (CIEM-FaMAF), Conicet. C\'ordoba. Argentina.
    Supported by Secyt-UNC project 33620180100465CB.}
  \and
  Mat\'{\i}as Steinberg\footnotemark[1]
}
\maketitle

@@

The main entry point of the present session is the theory
\theory{Defitions\_Main.thy}, in which a path from fundamental set
theoretic concepts formalized in Isabelle reaching our main theorems
is expounded. Cross-references to major milestones are provided there.

In order to provide evidence for the correctness of several of our relativized
definitions, we needed to assume the Axiom of Choice ($\AC$) during the
aforementioned theory. Nevertheless, the whole of our development is
independent of $\AC$, and the theory \theory{CH.thy} already provides
all of our results and does not import that axiom.
